\Large \bf \projtitle

### 2015-05-08 doc/paper/paper.tex
Fix

We tested \zbf on a simple site that loads one large 768KB image from a remote server.
In our tests, we compare page load times using both plain HTTP and \zbf in a range of
scenarios. Specifically, we varied two parameters: the number of seeding peers and the
number of leeching peers. A seeding peer is a peer that has the desired resource, which
in our tests, was the single image on the site. A leeching peer is a peer that desires the
resource, so must request it either from the central site host or from peers with the resource.

@@

\inclfigure{fig:heatmap}{heatmap.eps}{-90}{
    Average page load time over P2P for seeders vs leechers.
}

@@

\inclfigure{fig:scalability}{scalability.eps}{-90}{
    Average page load time over P2P compared to HTTP on throttled server
    assuming constant ratio of 1 seeder per leecher.
}

>>>>

We tested \zbf on a simple site that loads one large 768 KB image from a remote server.
In our tests, we compare page load times using both plain HTTP and \zbf in a range of
scenarios. Specifically, we varied two parameters: the number of seeding peers and the
number of leeching peers. A seeding peer is a peer that has the desired resource, which
in our tests, was the single image on the site. A leeching peer is a peer that desires the
resource, so must request it either from the central site host or from peers with the resource.

@@

\inclfigure{fig:heatmap}{heatmap.eps}{-90}{
    Average page load time (lower is better) over P2P for seeders vs leechers.
}

@@

\inclfigure{fig:scalability}{scalability.eps}{-90}{
    Average page load time (lower is better) over P2P compared to HTTP on
    throttled server assuming constant ratio of 1 seeder per leecher.
}
